---
output: pdf_document
---

\newpage

## Belwaspur - Jumrikanda

6073 metres

### Full flight

\includegraphics{a_1}

### Kilometer 1

\includegraphics{a_2}


### Kilometer 2

\includegraphics{a_3}


### Kilometer 3

\includegraphics{a_4}


### Kilometer 4

\includegraphics{a_5}


### Kilometer 5

\includegraphics{a_6}


### Kilometer 6

\includegraphics{a_7}


### Kilometer 7

\includegraphics{a_2}



### Additional plots

```{r}

g11

g21

g31

```


\newpage

## Dakhanwadi - Jumrikanda

5830 metres

### Full flight

\includegraphics{b_1}

### Kilometer 1

\includegraphics{b_2}


### Kilometer 2

\includegraphics{b_3}


### Kilometer 3

\includegraphics{b_4}


### Kilometer 4

\includegraphics{b_5}


### Kilometer 5

\includegraphics{b_6}


### Kilometer 6

\includegraphics{b_2}



### Additional plots

```{r}

g12

g22

g32

```


\newpage

## Baraula - Dharampani

9205 metres

### Full flight

\includegraphics{c_1}

### Kilometer 1

\includegraphics{c_2}


### Kilometer 2

\includegraphics{c_3}


### Kilometer 3

\includegraphics{c_4}


### Kilometer 4

\includegraphics{c_5}


### Kilometer 5

\includegraphics{c_6}


### Kilometer 6

\includegraphics{c_7}


### Kilometer 7

\includegraphics{c_8}


### Kilometer 8

\includegraphics{c_9}


### Kilometer 9

\includegraphics{c_10}


### Kilometer 10

\includegraphics{c_2}



### Additional plots

```{r}

g13

g23

g33

```


\newpage

## Sari - Swargadwarikhal

7811 metres

### Full flight

\includegraphics{d_1}

### Kilometer 1

\includegraphics{d_2}


### Kilometer 2

\includegraphics{d_3}


### Kilometer 3

\includegraphics{d_4}


### Kilometer 4

\includegraphics{d_5}


### Kilometer 5

\includegraphics{d_6}


### Kilometer 6

\includegraphics{d_7}


### Kilometer 7

\includegraphics{d_8}


### Kilometer 8

\includegraphics{d_2}



### Additional plots

```{r}

g14

g24

g34

```


\newpage

## Kochiwang - Swargadwarikhal

6166 metres

### Full flight

\includegraphics{e_1}

### Kilometer 1

\includegraphics{e_2}


### Kilometer 2

\includegraphics{e_3}


### Kilometer 3

\includegraphics{e_4}


### Kilometer 4

\includegraphics{e_5}


### Kilometer 5

\includegraphics{e_6}


### Kilometer 6

\includegraphics{e_7}


### Kilometer 7

\includegraphics{e_2}



### Additional plots

```{r}

g15

g25

g35

```


\newpage

## Dhobaghat(UdayapurKo - Gothiwang

6825 metres

### Full flight

\includegraphics{f_1}

### Kilometer 1

\includegraphics{f_2}


### Kilometer 2

\includegraphics{f_3}


### Kilometer 3

\includegraphics{f_4}


### Kilometer 4

\includegraphics{f_5}


### Kilometer 5

\includegraphics{f_6}


### Kilometer 6

\includegraphics{f_7}


### Kilometer 7

\includegraphics{f_2}



### Additional plots

```{r}

g16

g26

g36

```


\newpage

## Dhobaghat(UdayapurKo - Markawang

4162 metres

### Full flight

\includegraphics{g_1}

### Kilometer 1

\includegraphics{g_2}


### Kilometer 2

\includegraphics{g_3}


### Kilometer 3

\includegraphics{g_4}


### Kilometer 4

\includegraphics{g_5}


### Kilometer 5

\includegraphics{g_2}



### Additional plots

```{r}

g17

g27

g37

```


\newpage

## Dhobaghat(UdayapurKo - Nayagaun

4215 metres

### Full flight

\includegraphics{h_1}

### Kilometer 1

\includegraphics{h_2}


### Kilometer 2

\includegraphics{h_3}


### Kilometer 3

\includegraphics{h_4}


### Kilometer 4

\includegraphics{h_5}


### Kilometer 5

\includegraphics{h_2}



### Additional plots

```{r}

g18

g28

g38

```


\newpage

## Barjiwang - Jumrikanda

4242 metres

### Full flight

\includegraphics{i_1}

### Kilometer 1

\includegraphics{i_2}


### Kilometer 2

\includegraphics{i_3}


### Kilometer 3

\includegraphics{i_4}


### Kilometer 4

\includegraphics{i_5}


### Kilometer 5

\includegraphics{i_2}



### Additional plots

```{r}

g19

g29

g39

```


\newpage

## Jumrikanda - Phopli

5921 metres

### Full flight

\includegraphics{j_1}

### Kilometer 1

\includegraphics{j_2}


### Kilometer 2

\includegraphics{j_3}


### Kilometer 3

\includegraphics{j_4}


### Kilometer 4

\includegraphics{j_5}


### Kilometer 5

\includegraphics{j_6}


### Kilometer 6

\includegraphics{j_2}



### Additional plots

```{r}

g110

g210

g310

```


\newpage

## Damri - Khawang

6785 metres

### Full flight

\includegraphics{k_1}

### Kilometer 1

\includegraphics{k_2}


### Kilometer 2

\includegraphics{k_3}


### Kilometer 3

\includegraphics{k_4}


### Kilometer 4

\includegraphics{k_5}


### Kilometer 5

\includegraphics{k_6}


### Kilometer 6

\includegraphics{k_7}


### Kilometer 7

\includegraphics{k_2}



### Additional plots

```{r}

g111

g211

g311

```


\newpage

## Khawang - Ligha

5682 metres

### Full flight

\includegraphics{l_1}

### Kilometer 1

\includegraphics{l_2}


### Kilometer 2

\includegraphics{l_3}


### Kilometer 3

\includegraphics{l_4}


### Kilometer 4

\includegraphics{l_5}


### Kilometer 5

\includegraphics{l_6}


### Kilometer 6

\includegraphics{l_2}



### Additional plots

```{r}

g112

g212

g312

```


\newpage

## Khawang - Syauliwang

9167 metres

### Full flight

\includegraphics{m_1}

### Kilometer 1

\includegraphics{m_2}


### Kilometer 2

\includegraphics{m_3}


### Kilometer 3

\includegraphics{m_4}


### Kilometer 4

\includegraphics{m_5}


### Kilometer 5

\includegraphics{m_6}


### Kilometer 6

\includegraphics{m_7}


### Kilometer 7

\includegraphics{m_8}


### Kilometer 8

\includegraphics{m_9}


### Kilometer 9

\includegraphics{m_10}


### Kilometer 10

\includegraphics{m_2}



### Additional plots

```{r}

g113

g213

g313

```


\newpage

## Khawang - Rajbara

9255 metres

### Full flight

\includegraphics{n_1}

### Kilometer 1

\includegraphics{n_2}


### Kilometer 2

\includegraphics{n_3}


### Kilometer 3

\includegraphics{n_4}


### Kilometer 4

\includegraphics{n_5}


### Kilometer 5

\includegraphics{n_6}


### Kilometer 6

\includegraphics{n_7}


### Kilometer 7

\includegraphics{n_8}


### Kilometer 8

\includegraphics{n_9}


### Kilometer 9

\includegraphics{n_10}


### Kilometer 10

\includegraphics{n_2}



### Additional plots

```{r}

g114

g214

g314

```


\newpage

## Arkha - Khawang

11173 metres

### Full flight

\includegraphics{o_1}

### Kilometer 1

\includegraphics{o_2}


### Kilometer 2

\includegraphics{o_3}


### Kilometer 3

\includegraphics{o_4}


### Kilometer 4

\includegraphics{o_5}


### Kilometer 5

\includegraphics{o_6}


### Kilometer 6

\includegraphics{o_7}


### Kilometer 7

\includegraphics{o_8}


### Kilometer 8

\includegraphics{o_9}


### Kilometer 9

\includegraphics{o_10}


### Kilometer 10

\includegraphics{o_11}


### Kilometer 11

\includegraphics{o_12}


### Kilometer 12

\includegraphics{o_2}



### Additional plots

```{r}

g115

g215

g315

```


\newpage

## Khung - Puja

4466 metres

### Full flight

\includegraphics{p_1}

### Kilometer 1

\includegraphics{p_2}


### Kilometer 2

\includegraphics{p_3}


### Kilometer 3

\includegraphics{p_4}


### Kilometer 4

\includegraphics{p_5}


### Kilometer 5

\includegraphics{p_2}



### Additional plots

```{r}

g116

g216

g316

```


\newpage

## Liwang - Puja

2738 metres

### Full flight

\includegraphics{q_1}

### Kilometer 1

\includegraphics{q_2}


### Kilometer 2

\includegraphics{q_3}


### Kilometer 3

\includegraphics{q_2}



### Additional plots

```{r}

g117

g217

g317

```


\newpage

## Narikot - Puja

3561 metres

### Full flight

\includegraphics{r_1}

### Kilometer 1

\includegraphics{r_2}


### Kilometer 2

\includegraphics{r_3}


### Kilometer 3

\includegraphics{r_4}


### Kilometer 4

\includegraphics{r_2}



### Additional plots

```{r}

g118

g218

g318

```


\newpage

## Dharmawati - Lung

5914 metres

### Full flight

\includegraphics{s_1}

### Kilometer 1

\includegraphics{s_2}


### Kilometer 2

\includegraphics{s_3}


### Kilometer 3

\includegraphics{s_4}


### Kilometer 4

\includegraphics{s_5}


### Kilometer 5

\includegraphics{s_6}


### Kilometer 6

\includegraphics{s_2}



### Additional plots

```{r}

g119

g219

g319

```


\newpage

## Okharkot - Tusara

3653 metres

### Full flight

\includegraphics{t_1}

### Kilometer 1

\includegraphics{t_2}


### Kilometer 2

\includegraphics{t_3}


### Kilometer 3

\includegraphics{t_4}


### Kilometer 4

\includegraphics{t_2}



### Additional plots

```{r}

g120

g220

g320

```


\newpage

## Badikot - Okharkot

6477 metres

### Full flight

\includegraphics{u_1}

### Kilometer 1

\includegraphics{u_2}


### Kilometer 2

\includegraphics{u_3}


### Kilometer 3

\includegraphics{u_4}


### Kilometer 4

\includegraphics{u_5}


### Kilometer 5

\includegraphics{u_6}


### Kilometer 6

\includegraphics{u_7}


### Kilometer 7

\includegraphics{u_2}



### Additional plots

```{r}

g121

g221

g321

```


\newpage

## Okharkot - Wangemarot

7213 metres

### Full flight

\includegraphics{v_1}

### Kilometer 1

\includegraphics{v_2}


### Kilometer 2

\includegraphics{v_3}


### Kilometer 3

\includegraphics{v_4}


### Kilometer 4

\includegraphics{v_5}


### Kilometer 5

\includegraphics{v_6}


### Kilometer 6

\includegraphics{v_7}


### Kilometer 7

\includegraphics{v_8}


### Kilometer 8

\includegraphics{v_2}



### Additional plots

```{r}

g122

g222

g322

```


\newpage

## Chuja - Okharkot

4333 metres

### Full flight

\includegraphics{w_1}

### Kilometer 1

\includegraphics{w_2}


### Kilometer 2

\includegraphics{w_3}


### Kilometer 3

\includegraphics{w_4}


### Kilometer 4

\includegraphics{w_5}


### Kilometer 5

\includegraphics{w_2}



### Additional plots

```{r}

g123

g223

g323

```


\newpage

## Okharkot - Torwang

3971 metres

### Full flight

\includegraphics{x_1}

### Kilometer 1

\includegraphics{x_2}


### Kilometer 2

\includegraphics{x_3}


### Kilometer 3

\includegraphics{x_4}


### Kilometer 4

\includegraphics{x_2}



### Additional plots

```{r}

g124

g224

g324

```


\newpage

## Dharmawati - Maranthana

3839 metres

### Full flight

\includegraphics{y_1}

### Kilometer 1

\includegraphics{y_2}


### Kilometer 2

\includegraphics{y_3}


### Kilometer 3

\includegraphics{y_4}


### Kilometer 4

\includegraphics{y_2}



### Additional plots

```{r}

g125

g225

g325

```


\newpage

## Bijuli - Dharampani

5649 metres

### Full flight

\includegraphics{z_1}

### Kilometer 1

\includegraphics{z_2}


### Kilometer 2

\includegraphics{z_3}


### Kilometer 3

\includegraphics{z_4}


### Kilometer 4

\includegraphics{z_5}


### Kilometer 5

\includegraphics{z_6}


### Kilometer 6

\includegraphics{z_2}



### Additional plots

```{r}

g126

g226

g326

```


\newpage

## Dangwang - Dharampani

14037 metres

### Full flight

\includegraphics{aa_1}

### Kilometer 1

\includegraphics{aa_2}


### Kilometer 2

\includegraphics{aa_3}


### Kilometer 3

\includegraphics{aa_4}


### Kilometer 4

\includegraphics{aa_5}


### Kilometer 5

\includegraphics{aa_6}


### Kilometer 6

\includegraphics{aa_7}


### Kilometer 7

\includegraphics{aa_8}


### Kilometer 8

\includegraphics{aa_9}


### Kilometer 9

\includegraphics{aa_10}


### Kilometer 10

\includegraphics{aa_11}


### Kilometer 11

\includegraphics{aa_12}


### Kilometer 12

\includegraphics{aa_13}


### Kilometer 13

\includegraphics{aa_14}


### Kilometer 14

\includegraphics{aa_15}


### Kilometer 15

\includegraphics{aa_2}



### Additional plots

```{r}

g127

g227

g327

```


\newpage

## Dharampani - RuspurKot

3278 metres

### Full flight

\includegraphics{bb_1}

### Kilometer 1

\includegraphics{bb_2}


### Kilometer 2

\includegraphics{bb_3}


### Kilometer 3

\includegraphics{bb_4}


### Kilometer 4

\includegraphics{bb_2}



### Additional plots

```{r}

g128

g228

g328

```


\newpage

## Dharampani - Pakala

7266 metres

### Full flight

\includegraphics{cc_1}

### Kilometer 1

\includegraphics{cc_2}


### Kilometer 2

\includegraphics{cc_3}


### Kilometer 3

\includegraphics{cc_4}


### Kilometer 4

\includegraphics{cc_5}


### Kilometer 5

\includegraphics{cc_6}


### Kilometer 6

\includegraphics{cc_7}


### Kilometer 7

\includegraphics{cc_8}


### Kilometer 8

\includegraphics{cc_2}



### Additional plots

```{r}

g129

g229

g329

```


\newpage

## Hansapur - Tiram

10229 metres

### Full flight

\includegraphics{dd_1}

### Kilometer 1

\includegraphics{dd_2}


### Kilometer 2

\includegraphics{dd_3}


### Kilometer 3

\includegraphics{dd_4}


### Kilometer 4

\includegraphics{dd_5}


### Kilometer 5

\includegraphics{dd_6}


### Kilometer 6

\includegraphics{dd_7}


### Kilometer 7

\includegraphics{dd_8}


### Kilometer 8

\includegraphics{dd_9}


### Kilometer 9

\includegraphics{dd_10}


### Kilometer 10

\includegraphics{dd_11}


### Kilometer 11

\includegraphics{dd_2}



### Additional plots

```{r}

g130

g230

g330

```


\newpage

## Bangesal - Tiram

11483 metres

### Full flight

\includegraphics{ee_1}

### Kilometer 1

\includegraphics{ee_2}


### Kilometer 2

\includegraphics{ee_3}


### Kilometer 3

\includegraphics{ee_4}


### Kilometer 4

\includegraphics{ee_5}


### Kilometer 5

\includegraphics{ee_6}


### Kilometer 6

\includegraphics{ee_7}


### Kilometer 7

\includegraphics{ee_8}


### Kilometer 8

\includegraphics{ee_9}


### Kilometer 9

\includegraphics{ee_10}


### Kilometer 10

\includegraphics{ee_11}


### Kilometer 11

\includegraphics{ee_12}


### Kilometer 12

\includegraphics{ee_2}



### Additional plots

```{r}

g131

g231

g331

```


\newpage

## Dungegadi - Tiram

7089 metres

### Full flight

\includegraphics{ff_1}

### Kilometer 1

\includegraphics{ff_2}


### Kilometer 2

\includegraphics{ff_3}


### Kilometer 3

\includegraphics{ff_4}


### Kilometer 4

\includegraphics{ff_5}


### Kilometer 5

\includegraphics{ff_6}


### Kilometer 6

\includegraphics{ff_7}


### Kilometer 7

\includegraphics{ff_8}


### Kilometer 8

\includegraphics{ff_2}



### Additional plots

```{r}

g132

g232

g332

```


\newpage

## Dhuwang - Tiram

7850 metres

### Full flight

\includegraphics{gg_1}

### Kilometer 1

\includegraphics{gg_2}


### Kilometer 2

\includegraphics{gg_3}


### Kilometer 3

\includegraphics{gg_4}


### Kilometer 4

\includegraphics{gg_5}


### Kilometer 5

\includegraphics{gg_6}


### Kilometer 6

\includegraphics{gg_7}


### Kilometer 7

\includegraphics{gg_8}


### Kilometer 8

\includegraphics{gg_2}



### Additional plots

```{r}

g133

g233

g333

```


\newpage

## Dharampani - Khaira

7558 metres

### Full flight

\includegraphics{hh_1}

### Kilometer 1

\includegraphics{hh_2}


### Kilometer 2

\includegraphics{hh_3}


### Kilometer 3

\includegraphics{hh_4}


### Kilometer 4

\includegraphics{hh_5}


### Kilometer 5

\includegraphics{hh_6}


### Kilometer 6

\includegraphics{hh_7}


### Kilometer 7

\includegraphics{hh_8}


### Kilometer 8

\includegraphics{hh_2}



### Additional plots

```{r}

g134

g234

g334

```


\newpage

## Ramdi - Tiram

6244 metres

### Full flight

\includegraphics{ii_1}

### Kilometer 1

\includegraphics{ii_2}


### Kilometer 2

\includegraphics{ii_3}


### Kilometer 3

\includegraphics{ii_4}


### Kilometer 4

\includegraphics{ii_5}


### Kilometer 5

\includegraphics{ii_6}


### Kilometer 6

\includegraphics{ii_7}


### Kilometer 7

\includegraphics{ii_2}



### Additional plots

```{r}

g135

g235

g335

```


\newpage

## Baraula - Pakala

3601 metres

### Full flight

\includegraphics{jj_1}

### Kilometer 1

\includegraphics{jj_2}


### Kilometer 2

\includegraphics{jj_3}


### Kilometer 3

\includegraphics{jj_4}


### Kilometer 4

\includegraphics{jj_2}



### Additional plots

```{r}

g136

g236

g336

```


\newpage

## Rajbara - Syauliwang

6862 metres

### Full flight

\includegraphics{kk_1}

### Kilometer 1

\includegraphics{kk_2}


### Kilometer 2

\includegraphics{kk_3}


### Kilometer 3

\includegraphics{kk_4}


### Kilometer 4

\includegraphics{kk_5}


### Kilometer 5

\includegraphics{kk_6}


### Kilometer 6

\includegraphics{kk_7}


### Kilometer 7

\includegraphics{kk_2}



### Additional plots

```{r}

g137

g237

g337

```


\newpage

## Arkha - Rajbara

3305 metres

### Full flight

\includegraphics{ll_1}

### Kilometer 1

\includegraphics{ll_2}


### Kilometer 2

\includegraphics{ll_3}


### Kilometer 3

\includegraphics{ll_4}


### Kilometer 4

\includegraphics{ll_2}



### Additional plots

```{r}

g138

g238

g338

```


\newpage

## Baraula - Dangwang

5588 metres

### Full flight

\includegraphics{mm_1}

### Kilometer 1

\includegraphics{mm_2}


### Kilometer 2

\includegraphics{mm_3}


### Kilometer 3

\includegraphics{mm_4}


### Kilometer 4

\includegraphics{mm_5}


### Kilometer 5

\includegraphics{mm_6}


### Kilometer 6

\includegraphics{mm_2}



### Additional plots

```{r}

g139

g239

g339

```


\newpage

## Bangesal - Hansapur

2532 metres

### Full flight

\includegraphics{nn_1}

### Kilometer 1

\includegraphics{nn_2}


### Kilometer 2

\includegraphics{nn_3}


### Kilometer 3

\includegraphics{nn_2}



### Additional plots

```{r}

g140

g240

g340

```


