---
title: DrOTS Nepal Flight Plans
date: ''
output: 
  pdf_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
    keep_tex: true
    latex_engine: xelatex
    number_sections: true
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
csl: journal-of-health-economics.csl
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = FALSE}
# Packages
library(tidyverse)
library(knitr)
library(Hmisc)
library(knitr)
library(RColorBrewer)
library(extrafont)
library(databrew)
library(nepal)
library(sp)
library(leaflet)
library(mapview)
library(geosphere)
library(ggthemes)
library(ggrepel)
loadfonts()
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               dev = "cairo_pdf",
               fig.pos="H"#,
               # fig.path = 'figures/'
               )
opts_knit$set(width=75)
options(xtable.comment = FALSE)
```



\begin{center}
\begin{large}

```{r, results = 'asis', eval = TRUE}
cat(
  paste0(
    'DrOTS Nepal, Nepal Flying Labs, Birat Nepal Medical Trust'
  # 'Joe Brew\\footremember{db}{Databrew, Toronto, Canada}\\footremember{cism}{Centro de Investigação em Saúde de Manhiça: Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique, Mozambique} \\footnote{Corresponding Author}  Ben Brew\\footrecall{db}   Xing Brew\\footrecall{db}'
  )
)

```

\end{large}
\end{center}

\vspace{5mm}

\begin{center}
\textbf{Abstract}  
\end{center}

\vspace{5mm}
\begin{center}
\begin{changemargin}{3cm}{3cm} 

This document contains visuals of all planned flights in Pyuthan for the period from January 2019 through September 2019.

\end{changemargin}
\end{center}

\vspace{20mm}

\noindent\fbox{%
    \parbox{\textwidth}{%
        \subsection*{Contents}
        \begin{itemize}
          \item Overview map
          \item Flight specific strip maps
        \end{itemize}
        \vspace{2mm}
    }%
}

\vfill
\null



\vspace{3mm}

\newpage

# Overview  

The below map shows all flights planned in the Pyuthan district.

```{r}
# x <- hps <- nepal::pyuthan_health_facilities
# y <- hps[hps@data$HF_TYPE == 'Sub Health Post' |
#            (hps@data$VDC_NAME1 == 'Bijubar' &
#             hps@data$HF_TYPE == 'Hospital') | 
#             hps@data$VDC_NAME1 =='Swargadwarikhal' ,]
# y$hospital <- (y@data$VDC_NAME1 == 'Bijubar' &
#             y@data$HF_TYPE == 'Hospital') | 
#             y@data$VDC_NAME1 =='Swargadwarikhal'
# cc <- coordinates(y)
# cc <- data.frame(cc)
# names(cc) <- c('x', 'y')
# y@data <- bind_cols(y@data, cc)
# y$distances <- y$min_distance <- y$min_name <- y$route <- y$x_end <- y$y_end<- NA
# for(i in 1:nrow(y)){
#   x <- distGeo(p1 = y[i,],
#                             p2 = y)
#   closest_index <- order(x)[2]
#   closest_distance <- x[closest_index]
#   closest_name <- as.character(y$VDC_NAME1[closest_index])
#   closest_type <- as.character(y$HF_TYPE)
#   route <- sort(c(as.character(y$VDC_NAME1[i]),
#                 closest_name))
#   route <- paste0(route, collapse = ' - ')
#   y_end <- y@data$y[closest_index]
#   x_end <- y@data$x[closest_index]
#   # y$distances[i] <- list(x)
#   y$min_distance[i] <- closest_distance
#   y$min_name[i] <- closest_name
#   y$route[i] <- route
#   y$x_end[i] <- x_end
#   y$y_end[i] <- y_end
# }
# 
# 
# 
# only_short <- y@data #%>% dplyr::distinct(route, .keep_all = T)
# only_short <- only_short %>%
#   mutate(xmid = (x + x_end)/2,
#          ymid = (y+y_end)/2)
# only_short_single <- only_short %>% dplyr::distinct(route, .keep_all = T)
# ggplot(data = only_short) +
#   geom_point(aes(x = x,y=y,
#                  color = hospital)) +
#   geom_segment(data = only_short_single,
#                aes(x = x,
#            y = y,
#            xend = x_end,
#            yend = y_end)) +
#   geom_text_repel(
#     data = only_short_single,
#     aes(x = xmid,
#         y = ymid,
#         label = paste0(route, '\n',
#                        round(min_distance/1000, digits = 1),
#                        ' km')),
#     size = rel(2)
#   )
```

```{r, fig.height = 7}
library(nepal)
x <- hps <- nepal::pyuthan_health_facilities
y <- hps[hps@data$HF_TYPE %in%  c('Sub Health Post', 'Health Post') |
           (hps@data$VDC_NAME1 == 'Bijubar' &
            hps@data$HF_TYPE == 'Hospital') | 
            hps@data$VDC_NAME1 =='Swargadwarikhal' ,]
y$hospital <- (y@data$VDC_NAME1 == 'Bijubar' &
            y@data$HF_TYPE == 'Hospital') | 
            y@data$VDC_NAME1 =='Swargadwarikhal'
y$health_post <- y$HF_TYPE == 'Health Post'
y$sub_health_post <- y$HF_TYPE == 'Sub Health Post'
y$hub <- y$hospital | y$VDC_NAME1 == 'Khawang'
y$type <- ifelse(y$hub, 'Hub',
                 ifelse(y$health_post, 'Health post',
                        ifelse(y$sub_health_post, 'Sub health post', NA)))

cc <- coordinates(y)
cc <- data.frame(cc)
names(cc) <- c('x', 'y')
y@data <- bind_cols(y@data, cc)
y$distances <- y$min_distance <- y$min_name <- y$route <- y$x_end <- y$y_end<- NA
# for(i in 1:nrow(y)){
#   this_type <- y$type[i]
#   x <- distGeo(p1 = y[i,],p2 = y)
#   keep_index <- 1:nrow(y)
#   keep_index <- keep_index[keep_index != i]
#   # if(this_type == 'Sub health post'){
#   #   # keep_index <- which(y$health_post)
#   # }
#   hosp_index <- which.min(x[keep_index])
#   closest_index <- keep_index[hosp_index]
#   closest_distance <- x[closest_index]
#   closest_name <- as.character(y$VDC_NAME1[closest_index])
#   closest_type <- as.character(y$HF_TYPE)
#   route <- sort(c(as.character(y$VDC_NAME1[i]),
#                 closest_name))
#   route <- paste0(route, collapse = ' - ')
#   y_end <- y@data$y[closest_index]
#   x_end <- y@data$x[closest_index]
#   # y$distances[i] <- list(x)
#   y$min_distance[i] <- closest_distance
#   y$min_name[i] <- closest_name
#   y$route[i] <- route
#   y$x_end[i] <- x_end
#   y$y_end[i] <- y_end
# }

max_distance <- 8000

# Just do the hubs
z <- y
for(i in 1:nrow(z)){
  this_type <- z$type[i]
  x <- distGeo(p1 = z[i,],p2 = z)
  keep_index <- 1:nrow(z)
  # keep_index <- keep_index[keep_index != i]
  if(this_type == 'Sub health post'){
    keep_index <- which(z$health_post)
  }
  hosp_index <- which.min(x[keep_index])
  closest_index <- keep_index[hosp_index]
  closest_distance <- x[closest_index]
  closest_name <- as.character(z$VDC_NAME1[closest_index])
  closest_tzpe <- as.character(z$HF_TYPE)
  route <- sort(c(as.character(z$VDC_NAME1[i]),
                closest_name))
  route <- paste0(route, collapse = ' - ')
  y_end <- z@data$y[closest_index]
  x_end <- z@data$x[closest_index]
  # z$distances[i] <- list(x)
  z$min_distance[i] <- closest_distance
  z$min_name[i] <- closest_name
  z$route[i] <- route
  z$x_end[i] <- x_end
  z$y_end[i] <- y_end
}


# Repeat for extremes
# Repeat with the hubs
zz <- z
zz <- zz[zz@data$min_distance > max_distance,]
for(i in 1:nrow(zz)){
  this_type <- zz$type[i]
  this_name <- zz$VDC_NAME1[i]
  x <- distGeo(p1 = zz[i,],p2 = z)
  keep_index <- 1:length(x)
  keep_index <- keep_index[z$VDC_NAME1 != this_name]# &
                             # !z$VDC_NAME1 %in% zz$VDC_NAME1]
  # if(this_type == 'Sub health post'){
  #   keep_index <- which(zz$health_post)
  # }
  hosp_index <- which.min(x[keep_index])
  closest_index <- keep_index[hosp_index]
  closest_distance <- x[closest_index]
  closest_name <- as.character(z$VDC_NAME1[closest_index])
  route <- sort(c(as.character(zz$VDC_NAME1[i]),
                closest_name))
  route <- paste0(route, collapse = ' - ')
  y_end <- z@data$y[closest_index]
  x_end <- z@data$x[closest_index]
  # zz$distances[i] <- list(x)
  zz$min_distance[i] <- closest_distance
  zz$min_name[i] <- closest_name
  zz$route[i] <- route
  zz$x_end[i] <- x_end
  zz$y_end[i] <- y_end
}

only_short <- z@data %>% 
  # filter(min_distance <= max_distance) %>%
  bind_rows(zz@data) %>%
  filter(min_distance > 0)
only_short <- only_short %>%
  mutate(xmid = (x + x_end)/2,
         ymid = (y+y_end)/2)
only_short_single <- only_short %>% dplyr::distinct(route, .keep_all = T)


ggplot(data = only_short) +
  geom_polygon(data = pyuthan_fortified,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = 'grey',
               alpha = 0.4,
               lwd = 0.2,
               color = 'black') +
  geom_point(data = y@data,
             aes(x = x,y=y,
                 color = type),
             size = 2) +
  geom_text(data = y@data,
                   aes(x = x,y=y,
                       label = VDC_NAME1),
                  alpha = 0.6,
                  size = 3,
            nudge_y = 0.01) +
  # geom_point(aes(x = x,y=y,
  #                color = HF_TYPE)) +
  geom_segment(data = only_short_single,
               aes(x = x,
           y = y,
           xend = x_end,
           yend = y_end),
           color = 'red',
           alpha = 0.4) +
  geom_text(
    data = only_short_single,
    aes(x = xmid,
        y = ymid,
        label = paste0(#route, '\n',
                       round(min_distance/1000, digits = 1),
                       ' km')),
    size = rel(2.2),
    alpha = 0.6,
    color = 'darkred'
    # segment.colour = 'white'
  ) +
  theme_map() +
  scale_color_manual(name = '',
                     values = databrew::make_colors(3))

```

\newpage


# Strip maps

The below show strip maps (both complete and kilometer-specific) with a 500 meter buffer.

```{r}
flights <- only_short_single
flights$distance <- flights$min_distance
# flights <- flights %>% arrange(distance)

# flights <- flights[1,]
titles <- distances <- subtitles <- rep(NA, nrow(flights))
for(i in 1:nrow(flights)){
  if(i <= 26){
      this_letter <- letters[i]
    } else {
      this_letter <- paste0(rep(letters[i - 26], 2), collapse = '')
    }
    message('FLIGHT NUMBER ',i,'\nLETTER ', this_letter )

  sub_flight <- flights[i,]
  sub_df <- make_flight_path(x = c(sub_flight$x, sub_flight$x_end),
                           y = c(sub_flight$y, sub_flight$y_end))
  # sm <- make_strip_map(df = sub_df)
  sm <- as.list(1:ceiling(max(sub_df$d)/1000))
  g1 <- nepal::make_flight_path_elevation_plot(df = sub_df)
  g2 <- nepal::make_flight_path_plot(df = sub_df)
  g3 <- nepal::make_flight_path_population_plot(df = sub_df)
  assign(paste0('g1', i),
         g1,
         envir = .GlobalEnv)
  assign(paste0('g2', i),
         g2,
         envir = .GlobalEnv)
  assign(paste0('g3', i),
         g3,
         envir = .GlobalEnv)
  titles[i] <- sub_flight$route
  distances[i] <- sub_flight$distance
  
  # Save
  file_list <- list()
  for(z in 1:length(sm)){
    
    this_file_name <- paste0(this_letter, "_", z, ".png")

    file_name <- paste0(getwd(), '/', this_file_name)
  #   mapshot(sm[[z]], file = file_name,
  #       remove_controls = c("zoomControl", "layersControl", "homeButton",
  # "scaleBar"))
    file_list[[z]] <- this_file_name
  }
  file_list <- unlist(file_list)
  file_list <- gsub('.png', '', file_list, fixed = TRUE)
  if(length(file_list) == 1){
    subtitles[i] <- paste0('### Full flight\n\n\\includegraphics{', file_list, '}', collapse = '')
  } else {
    subtitles[i] <- 
      paste0('### Full flight\n\n\\includegraphics{',
             file_list[1],
             '}\n\n',
             paste0('### Kilometer ', 1:length(file_list), '\n\n\\includegraphics{',file_list[2:length(file_list)], '}\n\n' , collapse = '\n')
             )
  }
}

nums <- 1:nrow(flights)
content <- paste0('\\newpage\n\n## ', titles, '\n\n',
                  round(distances, digits = 0), ' metres\n\n',
                  
                  subtitles, '\n\n### Additional plots\n\n',
                  '```{r}\n\n',
                  paste0('g1', nums, '\n\n',
                         'g2', nums, '\n\n',
                         'g3', nums, '\n\n```\n\n')
                  )
```


```{r}
# Write our order / child-calls to a doc
file_connection <- file('babies.Rmd')
writeLines(paste0('---\noutput: pdf_document\n---\n\n', 
                  paste0(content, collapse = '\n'), collapse = '\n'), 
           file_connection)
close(file_connection)

```

```{r child='babies.Rmd', echo = FALSE}
```

```{r, results='hide'}
# file.remove('babies.Rmd')
```



