---
output: pdf_document
---

\newpage

## Barjiwang - Bijubar

9222 metres

### Full flight

\includegraphics{a_1}

### Kilometer 1

\includegraphics{a_2}


### Kilometer 2

\includegraphics{a_3}


### Kilometer 3

\includegraphics{a_4}


### Kilometer 4

\includegraphics{a_5}


### Kilometer 5

\includegraphics{a_6}


### Kilometer 6

\includegraphics{a_7}


### Kilometer 7

\includegraphics{a_8}


### Kilometer 8

\includegraphics{a_9}


### Kilometer 9

\includegraphics{a_10}


### Kilometer 10

\includegraphics{a_2}



### Additional plots

```{r}

g11

g21

g31

```


\newpage

## Belwaspur - Swargadwarikhal

15272 metres

### Full flight

\includegraphics{b_1}

### Kilometer 1

\includegraphics{b_2}


### Kilometer 2

\includegraphics{b_3}


### Kilometer 3

\includegraphics{b_4}


### Kilometer 4

\includegraphics{b_5}


### Kilometer 5

\includegraphics{b_6}


### Kilometer 6

\includegraphics{b_7}


### Kilometer 7

\includegraphics{b_8}


### Kilometer 8

\includegraphics{b_9}


### Kilometer 9

\includegraphics{b_10}


### Kilometer 10

\includegraphics{b_11}


### Kilometer 11

\includegraphics{b_12}


### Kilometer 12

\includegraphics{b_13}


### Kilometer 13

\includegraphics{b_14}


### Kilometer 14

\includegraphics{b_15}


### Kilometer 15

\includegraphics{b_16}


### Kilometer 16

\includegraphics{b_2}



### Additional plots

```{r}

g12

g22

g32

```


\newpage

## Bijubar - Dharampani

7057 metres

### Full flight

\includegraphics{c_1}

### Kilometer 1

\includegraphics{c_2}


### Kilometer 2

\includegraphics{c_3}


### Kilometer 3

\includegraphics{c_4}


### Kilometer 4

\includegraphics{c_5}


### Kilometer 5

\includegraphics{c_6}


### Kilometer 6

\includegraphics{c_7}


### Kilometer 7

\includegraphics{c_8}


### Kilometer 8

\includegraphics{c_2}



### Additional plots

```{r}

g13

g23

g33

```


\newpage

## Bijubar - Dharmawati

9853 metres

### Full flight

\includegraphics{d_1}

### Kilometer 1

\includegraphics{d_2}


### Kilometer 2

\includegraphics{d_3}


### Kilometer 3

\includegraphics{d_4}


### Kilometer 4

\includegraphics{d_5}


### Kilometer 5

\includegraphics{d_6}


### Kilometer 6

\includegraphics{d_7}


### Kilometer 7

\includegraphics{d_8}


### Kilometer 8

\includegraphics{d_9}


### Kilometer 9

\includegraphics{d_10}


### Kilometer 10

\includegraphics{d_2}



### Additional plots

```{r}

g14

g24

g34

```


\newpage

## Bijubar - Dhuwang

11263 metres

### Full flight

\includegraphics{e_1}

### Kilometer 1

\includegraphics{e_2}


### Kilometer 2

\includegraphics{e_3}


### Kilometer 3

\includegraphics{e_4}


### Kilometer 4

\includegraphics{e_5}


### Kilometer 5

\includegraphics{e_6}


### Kilometer 6

\includegraphics{e_7}


### Kilometer 7

\includegraphics{e_8}


### Kilometer 8

\includegraphics{e_9}


### Kilometer 9

\includegraphics{e_10}


### Kilometer 10

\includegraphics{e_11}


### Kilometer 11

\includegraphics{e_12}


### Kilometer 12

\includegraphics{e_2}



### Additional plots

```{r}

g15

g25

g35

```


\newpage

## Bijubar - Jumrikanda

9636 metres

### Full flight

\includegraphics{f_1}

### Kilometer 1

\includegraphics{f_2}


### Kilometer 2

\includegraphics{f_3}


### Kilometer 3

\includegraphics{f_4}


### Kilometer 4

\includegraphics{f_5}


### Kilometer 5

\includegraphics{f_6}


### Kilometer 6

\includegraphics{f_7}


### Kilometer 7

\includegraphics{f_8}


### Kilometer 8

\includegraphics{f_9}


### Kilometer 9

\includegraphics{f_10}


### Kilometer 10

\includegraphics{f_2}



### Additional plots

```{r}

g16

g26

g36

```


\newpage

## Bijubar - Maranthana

5426 metres

### Full flight

\includegraphics{g_1}

### Kilometer 1

\includegraphics{g_2}


### Kilometer 2

\includegraphics{g_3}


### Kilometer 3

\includegraphics{g_4}


### Kilometer 4

\includegraphics{g_5}


### Kilometer 5

\includegraphics{g_6}


### Kilometer 6

\includegraphics{g_2}



### Additional plots

```{r}

g17

g27

g37

```


\newpage

## Gothiwang - Swargadwarikhal

6129 metres

### Full flight

\includegraphics{h_1}

### Kilometer 1

\includegraphics{h_2}


### Kilometer 2

\includegraphics{h_3}


### Kilometer 3

\includegraphics{h_4}


### Kilometer 4

\includegraphics{h_5}


### Kilometer 5

\includegraphics{h_6}


### Kilometer 6

\includegraphics{h_7}


### Kilometer 7

\includegraphics{h_2}



### Additional plots

```{r}

g18

g28

g38

```


\newpage

## Kochiwang - Swargadwarikhal

6787 metres

### Full flight

\includegraphics{i_1}

### Kilometer 1

\includegraphics{i_2}


### Kilometer 2

\includegraphics{i_3}


### Kilometer 3

\includegraphics{i_4}


### Kilometer 4

\includegraphics{i_5}


### Kilometer 5

\includegraphics{i_6}


### Kilometer 6

\includegraphics{i_7}


### Kilometer 7

\includegraphics{i_2}



### Additional plots

```{r}

g19

g29

g39

```


\newpage

## Sari - Swargadwarikhal

10753 metres

### Full flight

\includegraphics{j_1}

### Kilometer 1

\includegraphics{j_2}


### Kilometer 2

\includegraphics{j_3}


### Kilometer 3

\includegraphics{j_4}


### Kilometer 4

\includegraphics{j_5}


### Kilometer 5

\includegraphics{j_6}


### Kilometer 6

\includegraphics{j_7}


### Kilometer 7

\includegraphics{j_8}


### Kilometer 8

\includegraphics{j_9}


### Kilometer 9

\includegraphics{j_10}


### Kilometer 10

\includegraphics{j_11}


### Kilometer 11

\includegraphics{j_2}



### Additional plots

```{r}

g110

g210

g310

```


