---
title: DrOTS Nepal Flight Plans
date: ''
output: 
  pdf_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
    keep_tex: true
    latex_engine: xelatex
    number_sections: true
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
csl: journal-of-health-economics.csl
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = FALSE}
# Packages
library(tidyverse)
library(knitr)
library(Hmisc)
library(knitr)
library(RColorBrewer)
library(extrafont)
library(databrew)
library(nepal)
library(sp)
library(leaflet)
library(mapview)
library(geosphere)
library(ggthemes)
library(ggrepel)
loadfonts()
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               dev = "cairo_pdf",
               fig.pos="H"#,
               # fig.path = 'figures/'
               )
opts_knit$set(width=75)
options(xtable.comment = FALSE)
```



\begin{center}
\begin{large}

```{r, results = 'asis', eval = TRUE}
cat(
  paste0(
    'DrOTS Nepal, Nepal Flying Labs, Birat Nepal Medical Trust'
  # 'Joe Brew\\footremember{db}{Databrew, Toronto, Canada}\\footremember{cism}{Centro de Investigação em Saúde de Manhiça: Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique, Mozambique} \\footnote{Corresponding Author}  Ben Brew\\footrecall{db}   Xing Brew\\footrecall{db}'
  )
)

```

\end{large}
\end{center}

\vspace{5mm}


\vspace{5mm}
\begin{center}
\begin{changemargin}{3cm}{3cm} 

This document contains visuals of and data relating to planned flights in Pyuthan for the period from January 2019 through September 2019.

\end{changemargin}
\end{center}

\vspace{20mm}

\noindent\fbox{%
    \parbox{\textwidth}{%
        \subsection*{Contents}
        \begin{itemize}
          \item Overview map
          \item Flight specific strip maps
        \end{itemize}
        \vspace{2mm}
    }%
}

\vfill
\null



\vspace{3mm}

\newpage

# Overview  

The below map shows all flights planned in the Pyuthan district.

```{r}
all_files <- dir('data')
file_list <- list()
for(i in 1:length(all_files)){
  message('reading file ', i, ' of ', length(all_files))
  this_file <- all_files[i]
  this_route <- gsub('.csv', '', this_file, fixed = TRUE)
  file_list[[i]] <-
    read_csv(paste0('data/',this_file)) %>% mutate(route = this_route)
}
all_flights <- bind_rows(file_list)
```

```{r, fig.height = 7}
x <- hps <- nepal::pyuthan_health_facilities
y <- hps[hps@data$HF_TYPE %in%  c('Sub Health Post', 'Health Post') |
           (hps@data$VDC_NAME1 == 'Bijubar' &
            hps@data$HF_TYPE == 'Hospital') | 
            hps@data$VDC_NAME1 =='Swargadwarikhal' ,]
y$hospital <- (y@data$VDC_NAME1 == 'Bijubar' &
            y@data$HF_TYPE == 'Hospital') | 
            y@data$VDC_NAME1 =='Swargadwarikhal'
y$health_post <- y$HF_TYPE == 'Health Post'
y$sub_health_post <- y$HF_TYPE == 'Sub Health Post'
y$hub <- y$hospital | y$VDC_NAME1 == 'Khawang'
y$type <- ifelse(y$hub, 'Hub',
                 ifelse(y$health_post, 'Health post',
                        ifelse(y$sub_health_post, 'Sub health post', NA)))
xy <- coordinates(y)
xy <- data.frame(xy)
names(xy) <- c('x', 'y')
y@data <- bind_cols(y@data, xy)
ggplot() +
  geom_polygon(data = pyuthan_fortified,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = 'grey',
               alpha = 0.4,
               lwd = 0.2,
               color = 'black') +
  geom_path(data = all_flights,
            aes(x = x,
                y = y,
                group = route),
            color = 'darkred') +
  geom_point(data = y@data,
             aes(x = x,y=y,
                 color = type),
             size = 2) +
  geom_text(data = y@data,
                   aes(x = x,y=y,
                       label = VDC_NAME1),
                  alpha = 0.6,
                  size = 3,
            nudge_y = 0.01) +

  theme_map() +
  scale_color_manual(name = '',
                     values = databrew::make_colors(3))

```

\newpage


# Strip maps

The below show strip maps (both complete and kilometer-specific) with a 500 meter buffer.

```{r}
flights <- all_flights
flights <- flights %>%
  group_by(route) %>%
  mutate(distance = max(d)) %>%
  ungroup
# flights <- flights %>% arrange(distance)

# flights <- flights[1,]
unique_flights <- unique(flights$route)
titles <- distances <- subtitles <- rep(NA, length(unique_flights))
for(i in 1:length(unique_flights)){
  this_flight <- unique_flights[i]
  if(i <= 26){
      this_letter <- letters[i]
    } else {
      this_letter <- paste0(rep(letters[i - 26], 2), collapse = '')
    }
    message('FLIGHT NUMBER ',i,'\nLETTER ', this_letter )

  sub_df <- flights %>%
    filter(route == this_flight)
  # sm <- make_strip_map(df = sub_df)
  sm <- as.list(1:ceiling(max(sub_df$d)/1000))
  g1 <- nepal::make_flight_path_elevation_plot(df = sub_df)
  g2 <- nepal::make_flight_path_plot(df = sub_df)
  g3 <- nepal::make_flight_path_population_plot(df = sub_df)
  assign(paste0('g1', i),
         g1,
         envir = .GlobalEnv)
  assign(paste0('g2', i),
         g2,
         envir = .GlobalEnv)
  assign(paste0('g3', i),
         g3,
         envir = .GlobalEnv)
  titles[i] <- sub_df$route[1]
  distances[i] <- sub_df$distance[1]
  
  # Save
  file_list <- list()
  for(z in 1:length(sm)){
    
    this_file_name <- paste0(this_letter, "_", z, ".png")

    file_name <- paste0(getwd(), '/', this_file_name)
  #   mapshot(sm[[z]], file = file_name,
  #       remove_controls = c("zoomControl", "layersControl", "homeButton",
  # "scaleBar"))
    file_list[[z]] <- this_file_name
  }
  file_list <- unlist(file_list)
  file_list <- gsub('.png', '', file_list, fixed = TRUE)
  if(length(file_list) == 1){
    subtitles[i] <- paste0('### Full flight\n\n\\includegraphics{', file_list, '}', collapse = '')
  } else {
    subtitles[i] <- 
      paste0('### Full flight\n\n\\includegraphics{',
             file_list[1],
             '}\n\n',
             paste0('### Kilometer ', 1:length(file_list), '\n\n\\includegraphics{',file_list[2:length(file_list)], '}\n\n' , collapse = '\n')
             )
  }
}

nums <- 1:length(unique_flights)
content <- paste0('\\newpage\n\n## ', titles, '\n\n',
                  round(distances, digits = 0), ' metres\n\n',
                  
                  subtitles, '\n\n### Additional plots\n\n',
                  '```{r}\n\n',
                  paste0('g1', nums, '\n\n',
                         'g2', nums, '\n\n',
                         'g3', nums, '\n\n```\n\n')
                  )
```


```{r}
# Write our order / child-calls to a doc
file_connection <- file('babies.Rmd')
writeLines(paste0('---\noutput: pdf_document\n---\n\n', 
                  paste0(content, collapse = '\n'), collapse = '\n'), 
           file_connection)
close(file_connection)

```

```{r child='babies.Rmd', echo = FALSE}
```

```{r, results='hide'}
# file.remove('babies.Rmd')
```



